A thesis draft

### 2018-09-27 draft.tex
Add part about Openstack

As in~\ref{chap:intro}, the creation of a full ETSI MANO compliant
architecture, following the suggestions described in RFC 7665, require the 
integration of multiple tools (some of them have been already briefly 
introduced in~\ref{chap:intro}). The tools were choosen after their 
analysis, where pro and cons have been studied and compared to the necessity of 
this thesis.

>>>>

As in~\ref{chap:intro}, the creation of a full ETSI MANO compliant
architecture, following the suggestions described in RFC 7665, require the 
integration of multiple tools (some of them have been already briefly 
introduced in~\ref{chap:intro}). The tools were choosen after their 
analysis, where pro and cons have been studied and compared to the necessity of 
this thesis. Since the project has been developed with the cloud provided by 
the University of Padua, Openstack has been used as base for our deployments.

\paragraph{Openstack} Created in ??\todo{Find out Openstack date of creation}, 
Openstack allows on-permise cloud installation, using bare-metal resources to 
provide common cloud services as object storage, virtual machine deploy, 
virtual networking. Furthermore its modularity offers the possibility to add 
additional components, even proprietary, to achieve a complete solution. 
\todo{Finish him! :D}
